LAGOS lake depth

### 2021-12-06 figures/00_maps.Rmd
cleanup fig 2

```{r gg_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
bathy_pnts <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt         <- st_read("../data/gis.gpkg", "dt", quiet = TRUE)
max_depth <- dt$lake_maxdepth_m
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
dt <- dt %>%
  mutate(lake_maxdepth_m = round(lake_maxdepth_m, 2)) %>%
  mutate(maxdepth_class =
    smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, max(max_depth)),
      brackets = NULL, sep = " - ")
  ) %>% # unique(dt$maxdepth_class)
  dplyr::filter(!is.na(maxdepth_class))

@@

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.5}
theme_opts <- guides(color = guide_legend(
  override.aes = list(size = 2)))
cowplot::plot_grid(gg_bathy + theme_opts,
  gg_shapeclass + theme_opts,
  gg_reservoir + theme_opts,
  ncol = 1)
```

>>>>

```{r gg_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
bathy_pnts <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt         <- st_read("../data/gis.gpkg", "dt", quiet = TRUE)
max_depth <- dt$lake_maxdepth_m
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
dt <- dt %>%
  mutate(lake_maxdepth_m = round(lake_maxdepth_m, 2)) %>%
  mutate(maxdepth_class =
    smart_cut(lake_maxdepth_m, c(10, 30, 70, 200, max(max_depth)),
      brackets = NULL, sep = "-")
  ) %>% # unique(dt$maxdepth_class)
  dplyr::filter(!is.na(maxdepth_class))

@@

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6.5}
theme_opts <- guides(color = guide_legend(
  override.aes = list(size = 2)))
cowplot::plot_grid(gg_bathy + theme_opts,
  gg_shapeclass + theme_opts,
  gg_reservoir + theme_opts,
  labels = c("a", "b", "c"),
  label_x = 0.16,
  ncol = 1)
```
